---
title: "Poster Scripts"
author: "Brooke Sevchik"
date: "7/17/2023"
output: html_document
---


```{r data manipulation, OOO Plot 1.2 Anxiety}
ooo_anxiety_df

ooo_anxiety_binned_df <- ooo_anxiety_df %>%
  mutate(anxiety_binned = case_when(
    anxiety_level == 'low trait anxiety' | anxiety_level == 'moderate trait anxiety' ~ 'low to moderate trait anxiety',
    anxiety_level == 'high trait anxiety' ~ 'high trait anxiety'
  ))
ooo_anxiety_binned_df

threat_percent_anxiety_binned_df <- ooo_anxiety_binned_df  %>%
  group_by(subject) %>% 
  summarise(n_chose_threat = sum(chosenThreatStatus == 'threat'), n_total = n(), percentage_chose_threat = n_chose_threat/n_total, anxiety_binned = anxiety_binned)
threat_percent_anxiety_binned_df

#high anxiety data frame, ooo first plot
high_anxiety_bin_threat_df <- threat_percent_anxiety_binned_df %>%
  filter(anxiety_binned == 'high trait anxiety')
high_anxiety_bin_threat_df

#low to moderate anxiety data frame, ooo first plot
low_moderate_anxiety_bin_threat_df <- threat_percent_anxiety_binned_df %>%
  filter(anxiety_binned == 'low to moderate trait anxiety')
low_moderate_anxiety_bin_threat_df



#GRAPHS
threat_percent_anxiety_binned_df <- threat_percent_anxiety_binned_df[!is.na(threat_percent_anxiety_binned_df$chosenThreatStatus), ]

ggplot(data = threat_percent_anxiety_binned_df, mapping = aes(x = chosenThreatStatus, y = percentage_chosenThreatStatus, fill = anxiety_binned)) +
  geom_boxplot(alpha = 0.5, outlier.shape = NA) +
  #geom_jitter(position = position_jitter(width = 0.05)) +
  geom_point(position = position_jitterdodge(jitter.width = 0.1)) +
  labs(title = "% Each Subject Chose Threat vs. Neutral Inaccurate Images in Odd One Out Task", x = "Chosen Threat Status", y = "Percentage")


#STATS
##PAIRED T TEST
t.test(threat_percent_anxiety_binned_df$percentage_chosenThreatStatus ~ threat_percent_anxiety_binned_df$chosenThreatStatus, mu = 0,
       alternative = "greater",
       paired = FALSE,
       var.equal = FALSE,
       conf.level = 0.95)


##ANOVA TO ADD STAI SCORES IN

# Create a new data frame with the desired groups
grouped_data <- subset(threat_percent_anxiety_binned_df, 
                       (chosenThreatStatus == "threat" & 
                          anxiety_binned %in% c("high trait anxiety", "low to moderate trait anxiety")) |
                         (chosenThreatStatus == "neutral" & 
                            anxiety_binned %in% c("high trait anxiety", "low to moderate trait anxiety")))

# Perform ANOVA
model <- aov(percentage_chosenThreatStatus ~ chosenThreatStatus * anxiety_binned, data = grouped_data)

# Print the ANOVA table
summary(model)

```
We investigated, for the trials in which the participant chose incorrectly in the odd one out task, and the other incorrect option of the three was of the opposite valence of the chosen incorrect image, were the participants more likely to choose the threat incorrect option or the neutral incorrect option?

There was no significant difference between the mean percentage that a subject chose a threat over a neutral image in these trials (p = 0.4778 > 0.05, paired t-test).
There was no significant difference modulated by trait anxiety level in mean percentage that a subject chose a threat over a neutral image in these trials, or significant interaction between trait anxiety level and mean percentage a subject chose a threat over a neutral image.





```{r data manipulation, OOO Plot 1.2 Anxiety}
subject_dprime_anxiety_df <- illegal_anxiety_df %>%
  select(subject, transition_threat, dprime, anxiety_level)
subject_dprime_anxiety_df

dprime_anxiety_binned_df <- subject_dprime_anxiety_df %>%
  mutate(anxiety_binned = case_when(
    anxiety_level == 'low trait anxiety' | anxiety_level == 'moderate trait anxiety' ~ 'low to moderate trait anxiety',
    anxiety_level == 'high trait anxiety' ~ 'high trait anxiety'
  ))
dprime_anxiety_binned_df


#GRAPHS
ggplot(dprime_anxiety_binned_df, aes(x = transition_threat, y = dprime, fill=anxiety_binned)) +
  geom_boxplot(alpha=0.5, outlier.shape = NA) +
  geom_jitter(width=0.1) +
  labs(title = "D Prime by Transition Type in Illegal Transition Task", x = "Transition Type", y = "D Prime Score",
       fill = "Transition Type") +
  scale_fill_manual(values = c("high trait anxiety" = "red", "low to moderate trait anxiety" = "blue"),
    labels = c("High Trait Anxiety", "Low to Moderate Trait Anxiety"))

##PAIRED T TEST
dprime_anxiety_binned_df

t.test(dprime_anxiety_binned_df$dprime ~ dprime_anxiety_binned_df$transition_threat, mu = 0,
       alternative = "greater",
       paired = TRUE,
       var.equal = FALSE,
       conf.level = 0.95)


##ANOVA TO ADD STAI SCORES IN
# Create a new data frame with the desired groups
grouped_data <- subset(dprime_anxiety_binned_df, 
                       (transition_threat == "contains_threat" & 
                          anxiety_binned %in% c("high trait anxiety", "low to moderate trait anxiety")) |
                         (transition_threat == "no_threat" & 
                            anxiety_binned %in% c("high trait anxiety", "low to moderate trait anxiety")))

# Perform ANOVA
model <- aov(dprime ~ transition_threat * anxiety_binned, data = grouped_data)

# Print the ANOVA table
summary(model)
```
There is a significant difference between mean d’ scores for transition involving a threat image versus transitions only involving neutral images (p = 0.0004357 > 0.05, paired t-test).

Participants with high trait anxiety have significantly higher d'scores overall, but this is not modulated by threat versus neutral images, as there is no interaction between whether or not a transition involves a threat image and trait anxiety score.



```{r data manipulation, OOO Plot 1.2 Anxiety}
check_answer_percent_summary_STAI

#filter out the last 3 trials of each subject
check_answer_percent_summary_STAI %>%
  group_by(subject) %>%
  mutate(last_trial = )


subject_dprime_anxiety_df <- illegal_anxiety_df %>%
  select(subject, transition_threat, dprime, anxiety_level)
subject_dprime_anxiety_df

dprime_anxiety_binned_df <- subject_dprime_anxiety_df %>%
  mutate(anxiety_binned = case_when(
    anxiety_level == 'low trait anxiety' | anxiety_level == 'moderate trait anxiety' ~ 'low to moderate trait anxiety',
    anxiety_level == 'high trait anxiety' ~ 'high trait anxiety'
  ))
dprime_anxiety_binned_df


#GRAPHS
ggplot(dprime_anxiety_binned_df, aes(x = transition_threat, y = dprime, fill=anxiety_binned)) +
  geom_boxplot(alpha=0.5) +
  geom_jitter(width=0.1) +
  labs(title = "D Prime by Transition Type in Illegal Transition Task", x = "Transition Type", y = "D Prime Score",
       fill = "Transition Type") +
  scale_fill_manual(values = c("high trait anxiety" = "red", "low to moderate trait anxiety" = "blue"),
    labels = c("High Trait Anxiety", "Low to Moderate Trait Anxiety"))

##PAIRED T TEST
dprime_anxiety_binned_df

t.test(dprime_anxiety_binned_df$dprime ~ dprime_anxiety_binned_df$transition_threat, mu = 0,
       alternative = "greater",
       paired = TRUE,
       var.equal = FALSE,
       conf.level = 0.95)


##ANOVA TO ADD STAI SCORES IN
# Create a new data frame with the desired groups
grouped_data <- subset(dprime_anxiety_binned_df, 
                       (transition_threat == "contains_threat" & 
                          anxiety_binned %in% c("high trait anxiety", "low to moderate trait anxiety")) |
                         (transition_threat == "no_threat" & 
                            anxiety_binned %in% c("high trait anxiety", "low to moderate trait anxiety")))

# Perform ANOVA
model <- aov(dprime ~ transition_threat * anxiety_binned, data = grouped_data)

# Print the ANOVA table
summary(model)
```






```{r data manipulation, OOO Plot 1.2 Anxiety}
check_answer_percent_summary_STAI

#filter out the last 3 trials of each subject
#check_answer_percent_summary_STAI %>%
  #group_by(subject) %>%
  #mutate(last_trial = )


subject_dprime_anxiety_df <- illegal_anxiety_df %>%
  select(subject, transition_threat, dprime, anxiety_level)
subject_dprime_anxiety_df

dprime_anxiety_binned_df <- subject_dprime_anxiety_df %>%
  mutate(anxiety_binned = case_when(
    anxiety_level == 'low trait anxiety' | anxiety_level == 'moderate trait anxiety' ~ 'low to moderate trait anxiety',
    anxiety_level == 'high trait anxiety' ~ 'high trait anxiety'
  ))
dprime_anxiety_binned_df


#GRAPHS
ggplot(dprime_anxiety_binned_df, aes(x = transition_threat, y = dprime, fill=anxiety_binned)) +
  geom_boxplot(alpha=0.5) +
  geom_jitter(width=0.1) +
  labs(title = "D Prime by Transition Type in Illegal Transition Task", x = "Transition Type", y = "D Prime Score",
       fill = "Transition Type") +
  scale_fill_manual(values = c("high trait anxiety" = "red", "low to moderate trait anxiety" = "blue"),
    labels = c("High Trait Anxiety", "Low to Moderate Trait Anxiety"))

##PAIRED T TEST
dprime_anxiety_binned_df

t.test(dprime_anxiety_binned_df$dprime ~ dprime_anxiety_binned_df$transition_threat, mu = 0,
       alternative = "greater",
       paired = TRUE,
       var.equal = FALSE,
       conf.level = 0.95)


##ANOVA TO ADD STAI SCORES IN
# Create a new data frame with the desired groups
grouped_data <- subset(dprime_anxiety_binned_df, 
                       (transition_threat == "contains_threat" & 
                          anxiety_binned %in% c("high trait anxiety", "low to moderate trait anxiety")) |
                         (transition_threat == "no_threat" & 
                            anxiety_binned %in% c("high trait anxiety", "low to moderate trait anxiety")))

# Perform ANOVA
model <- aov(dprime ~ transition_threat * anxiety_binned, data = grouped_data)

# Print the ANOVA table
summary(model)
```

```{r data manipulation, OOO Plot 1.2 Anxiety}
# Combine data frames for all subjects
subject_index <- which(names(avg_check_answer_acc_df_list) == "a3uv55hc87do9c")
subject_index

combined_df <- do.call(rbind, avg_check_answer_acc_df_list[-subject_index])



# Calculate average values for threat and neutral
average_df <- combined_df %>%
  group_by(trialCount) %>%
  summarize(threat = mean(threat), neutral = mean(neutral))

# Make the average plot
plot <- ggplot(average_df) +
  geom_line(aes(x = trialCount, y = threat, color = "Threat"), size = 1.6) +
  geom_line(aes(x = trialCount, y = neutral, color = "Neutral"), size = 1.6) +
  geom_point(aes(x = trialCount, y = threat, color = "Threat"), size = 1.6) +
  geom_point(aes(x = trialCount, y = neutral, color = "Neutral"), size = 1.6) +
  labs(title = "Average Plot", x = "Trial", y = "Accuracy (%)") +
  scale_color_manual(values = c(Threat = "red", Neutral = "blue"))


# Print the average plot
print(plot)


#plot for average across subjects
plot_avg <- plot
plot_avg

# Iterate through each subject's data frame and add semi-transparent thin lines to the plot_avg
for (subject in unique_subjects) {
  # Get data frame for the current subject
  subject_df <- avg_check_answer_acc_df_list[[subject]]
  
  # Check the maximum trial count for the current subject
  if (max(subject_df$trialCount) != 4 && subject != "a3uv55hc87do9c") {
    # Add semi-transparent lines for the current subject to the plot_avg
    plot_avg <- plot_avg +
      geom_line(data = subject_df, aes(x = trialCount, y = threat), color = "red", alpha = 0.3) +
      geom_line(data = subject_df, aes(x = trialCount, y = neutral), color = "blue", alpha = 0.3)
  }
}

# Display the plot_avg
plot_avg
```









