---
title: "Poster Scripts"
author: "Brooke Sevchik"
date: "7/17/2023"
output: html_document
---



```{r data manipulation, Odd One Out Task}
ooo_anxiety_df

ooo_anxiety_binned_df <- ooo_anxiety_df %>%
  mutate(anxiety_binned = case_when(
    anxiety_level == 'low trait anxiety' | anxiety_level == 'moderate trait anxiety' ~ 'low to moderate trait anxiety',
    anxiety_level == 'high trait anxiety' ~ 'high trait anxiety'
  ))
ooo_anxiety_binned_df

threat_percent_anxiety_binned_df <- ooo_anxiety_binned_df  %>%
  group_by(subject) %>% 
  summarise(n_chose_threat = sum(chosenThreatStatus == 'threat'), n_total = n(), percentage_chose_threat = n_chose_threat/n_total, anxiety_binned = anxiety_binned, chosenThreatStatus= chosenThreatStatus) %>%
  na.omit()
threat_percent_anxiety_binned_df

#neutral_percent_anxiety_binned_df <- ooo_anxiety_binned_df %>%
  #group_by(subject) %>%
  #summarise(n_chose_neutral = sum(chosenThreatStatus == 'neutral'), n_total = n(), percentage_chose_neutral = n_chose_neutral/n_total, anxiety_binned = anxiety_binned)
#neutral_percent_anxiety_binned_df


#GRAPHS
ggplot(data = threat_percent_anxiety_binned_df, mapping = aes(x = anxiety_binned, y = percentage_chose_threat, fill = anxiety_binned)) +
  geom_boxplot(alpha = 0.5, outlier.shape = NA) +
  #geom_jitter(position = position_jitter(width = 0.05)) +
  geom_point(position = position_jitterdodge(jitter.width = 0.3)) +
  geom_hline(yintercept = 0.5, linetype = "dotted", color = "red")+
  labs(title = "% Each Subject Chose Threat over Neutral Inaccurate Images in Odd One Out Task", x = "Anxiety Level", y = "Percentage")


#T-TEST - OVERALL
#calculate the mean and standard deviation
mean_percentage_chose_threat <- mean(threat_percent_anxiety_binned_df$percentage_chose_threat)
sd_percentage_chose_threat <- sd(threat_percent_anxiety_binned_df$percentage_chose_threat)

#one-sample t-test
t_test_result <- t.test(threat_percent_anxiety_binned_df$percentage_chose_threat, mu = 0.5)

#print result
print(t_test_result)


#T-TEST FOR EACH ANXIETY LEVEL
#create high anxiety df
threat_percent_high_anxiety_binned <- threat_percent_anxiety_binned_df %>%
  filter(anxiety_binned == 'high trait anxiety')
threat_percent_high_anxiety_binned

#calculate the mean and standard deviation
mean_percentage_chose_threat <- mean(threat_percent_high_anxiety_binned$percentage_chose_threat)
sd_percentage_chose_threat <- sd(threat_percent_high_anxiety_binned$percentage_chose_threat)
#one-sample t-test
t_test_result <- t.test(threat_percent_high_anxiety_binned$percentage_chose_threat, mu = 0.5, alternative = "greater")
#print result
print(t_test_result)


#creaet low to moderate anxiety df
threat_percent_low_anxiety_binned <- threat_percent_anxiety_binned_df %>%
  filter(anxiety_binned == 'low to moderate trait anxiety')
threat_percent_low_anxiety_binned

#calculate the mean and standard deviation
mean_percentage_chose_threat <- mean(threat_percent_low_anxiety_binned$percentage_chose_threat)
sd_percentage_chose_threat <- sd(threat_percent_low_anxiety_binned$percentage_chose_threat)
#one-sample t-test
t_test_result <- t.test(threat_percent_low_anxiety_binned$percentage_chose_threat, mu = 0.5, alternative = "greater")
#print result
print(t_test_result)




#showing overall accuracy/ceiling effect:

STAI_subject_acc_ooo_df

STAI_binned_acc_ooo <- STAI_subject_acc_ooo_df %>%
  mutate(anxiety_binned = case_when(
    anxiety_level == 'low trait anxiety' | anxiety_level == 'moderate trait anxiety' ~ 'low to moderate trait anxiety',
    anxiety_level == 'high trait anxiety' ~ 'high trait anxiety'
  ))
STAI_binned_acc_ooo

ggplot(STAI_binned_acc_ooo, aes(x = chosenThreatStatus, y = mean_acc, fill = anxiety_binned))+
  geom_boxplot(alpha = 0.5, outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.1)) +
  labs(title = "Mean Accuracy by Subject in OOO by CHosen Threat and Anxiety", x = "Chosen Threat Status", y = "Mean Accuracy")

```
We investigated, for the trials in which the participant chose incorrectly in the odd one out task, and the other incorrect option of the three was of the opposite valence of the chosen incorrect image, were the participants more likely to chosoe the threat incorrect option or the neutral incorrect option?
To do so, we compared their percentage/likelihood of picking the threat incorrect option to chance (50%).
There was no significant percentage over chance (50%) that a subject chose a threat over a neutral image in these trials.
This was not modulated by trait anxiety level either; there was no significant percentage over chance that a high anxiety or a low to moderate trait anxiety subject would choose a threat over a neutral images in these trials, as evidenced by separate one-sample t-tests for the low to moderate anxiety group and the high anxiety group.
This demonstrates a "ceiling effect," since everyone generally did really well on the task.
The last graph demonstrates how well people did on the task to show this "ceiling effect."


#We investigated, for the trials in which the participant chose incorrectly in the odd one out task, and the other incorrect option of the three was of the opposite valence of the chosen incorrect image, were the participants more likely to choose the threat incorrect option or the neutral incorrect option?

#There was no significant difference between the mean percentage that a subject chose a threat over a neutral image in these trials (p = 0.4778 > 0.05, paired t-test).
#There was no significant difference modulated by trait anxiety level in mean percentage that a subject chose a threat over a neutral image in these trials, or significant interaction between trait anxiety level and mean percentage a subject chose a threat over a neutral image.





```{r data manipulation, Illegal Transition Task}
subject_dprime_anxiety_df <- illegal_anxiety_df %>%
  select(subject, transition_threat, dprime, anxiety_level)
subject_dprime_anxiety_df

dprime_anxiety_binned_df <- subject_dprime_anxiety_df %>%
  mutate(anxiety_binned = case_when(
    anxiety_level == 'low trait anxiety' | anxiety_level == 'moderate trait anxiety' ~ 'low to moderate trait anxiety',
    anxiety_level == 'high trait anxiety' ~ 'high trait anxiety'
  ))
dprime_anxiety_binned_df


#GRAPHS
ggplot(dprime_anxiety_binned_df, aes(x = transition_threat, y = dprime, fill = anxiety_binned)) +
  geom_boxplot(alpha = 0.5, outlier.shape = NA) +
  #geom_jitter(width = 0.1) +
  geom_point(position = position_jitterdodge(jitter.width = 0.1)) +
  labs(title = "D Prime by Transition Type in Illegal Transition Task", x = "Transition Type", y = "D Prime Score",
       fill = "Transition Type") +
  scale_fill_manual(values = c("high trait anxiety" = "red", "low to moderate trait anxiety" = "blue"),
                    labels = c("High Trait Anxiety", "Low to Moderate Trait Anxiety"))



##PAIRED T TEST
dprime_anxiety_binned_df

t.test(dprime_anxiety_binned_df$dprime ~ dprime_anxiety_binned_df$transition_threat, mu = 0,
       alternative = "greater",
       paired = TRUE,
       var.equal = FALSE,
       conf.level = 0.95)


##ANOVA TO ADD STAI SCORES IN
# Create a new data frame with the desired groups
grouped_data <- subset(dprime_anxiety_binned_df, 
                       (transition_threat == "contains_threat" & 
                          anxiety_binned %in% c("high trait anxiety", "low to moderate trait anxiety")) |
                         (transition_threat == "no_threat" & 
                            anxiety_binned %in% c("high trait anxiety", "low to moderate trait anxiety")))

# Perform ANOVA
model <- aov(dprime ~ transition_threat * anxiety_binned, data = grouped_data)

# Print the ANOVA table
summary(model)


#check the means to see which is higher
dprime_anxiety_binned_df_means <- dprime_anxiety_binned_df %>%
  group_by(anxiety_binned) %>%
  summarise(mean_dprime = mean(dprime, na.rm = TRUE))
dprime_anxiety_binned_df_means

```
There is a significant difference between mean d’ scores for transition involving a threat image versus transitions only involving neutral images (p = 0.0004357 > 0.05, paired t-test).

Participants with high trait anxiety have significantly higher d'scores overall (mean dprime 3.19 significantly greater than mean dprime 2.88), but this is not modulated by threat versus neutral images, as there is no interaction between whether or not a transition involves a threat image and trait anxiety score.


```{r}
check_answer_percent_summary_STAI

exclude_df <- check_answer_percent_summary_STAI %>%
  filter(threat_status == 'equal') %>%
  filter(percentage == 100)
exclude_df

check_answer_percent_STAI_filtered <- check_answer_percent_summary_STAI %>%
  filter(!(subject %in% exclude_df$subject))
check_answer_percent_STAI_filtered

check_answer_percent_STAI_binned <- check_answer_percent_STAI_filtered %>%
  mutate(anxiety_binned = case_when(
    anxiety_level == 'low trait anxiety' | anxiety_level == 'moderate trait anxiety' ~ 'low to moderate trait anxiety',
    anxiety_level == 'high trait anxiety' ~ 'high trait anxiety'
  ))
check_answer_percent_STAI_binned


#GRAPHS
ggplot(check_answer_percent_STAI_binned, aes(x = threat_status, y = percentage, fill=anxiety_binned)) +
  geom_boxplot(alpha=0.5) +
  #geom_jitter(width=0.1) +
  geom_point(position = position_jitterdodge(jitter.width = 0.1)) +
  labs(title = "Check Answer Graph", x = "Threat Status", y = "Percentage",
       fill = "Anxiety Level") +
  scale_fill_manual(values = c("high trait anxiety" = "red", "low to moderate trait anxiety" = "blue"),
    labels = c("High Trait Anxiety", "Low to Moderate Trait Anxiety"))

##PAIRED T TEST

#exclude the 'equal' cases to just compare threat vs. neutral in t-test
check_answer_percent_STAI_binned_2 <- check_answer_percent_STAI_binned %>%
  filter(threat_status == 'threat' | threat_status == 'neutral')
check_answer_percent_STAI_binned_2


t.test(check_answer_percent_STAI_binned_2$percentage ~ check_answer_percent_STAI_binned_2$threat_status, mu = 0,
       alternative = "greater",
       paired = TRUE,
       var.equal = FALSE,
       conf.level = 0.95)


##ANOVA TO ADD STAI SCORES IN
# Create a new data frame with the desired groups
grouped_data <- subset(check_answer_percent_STAI_binned_2, 
                       (threat_status == "threat" & 
                          anxiety_binned %in% c("high trait anxiety", "low to moderate trait anxiety")) |
                         (threat_status == "neutral" & 
                            anxiety_binned %in% c("high trait anxiety", "low to moderate trait anxiety")))

# Perform ANOVA
model <- aov(percentage ~ threat_status * anxiety_binned, data = grouped_data)

# Print the ANOVA table
summary(model)



#check the means to see which is higher
percentage_anxiety_binned_df_means <- check_answer_percent_STAI_binned %>%
  group_by(threat_status) %>%
  summarise(mean_percentage = mean(percentage, na.rm = TRUE))
percentage_anxiety_binned_df_means
```

Threat mean > % than neutral mean
Which threat type is 100% correct first in the initial learning phase drag and drop task? Did people generally learn the threat images faster, i.e., across trials the percentage probability did they learn it 100% first more likely for threat images or neutral images?

The vast majority of trials for each subject, each person got threat and neutral ianges all correct at the same time, i.e., within the same trial.
The percentage that they learned all threat images first is significantly larger than the percentage that they learned all neutral images first. This is not modulated by anxiety, and people with high versus low to moderate anxiety generally did not influence the percentage they learned all threat images first before neutral images.



```{r data manipulation, OOO Plot 1.2 Anxiety}
# Combine data frames for all subjects
subject_index <- which(names(avg_check_answer_acc_df_list) == "a3uv55hc87do9c")
subject_index

combined_df <- do.call(rbind, avg_check_answer_acc_df_list[-subject_index])



# Calculate average values for threat and neutral
average_df <- combined_df %>%
  group_by(trialCount) %>%
  summarize(threat = mean(threat), neutral = mean(neutral))

# Make the average plot
plot <- ggplot(average_df) +
  geom_line(aes(x = trialCount, y = threat, color = "Threat"), size = 1.6) +
  geom_line(aes(x = trialCount, y = neutral, color = "Neutral"), size = 1.6) +
  geom_point(aes(x = trialCount, y = threat, color = "Threat"), size = 1.6) +
  geom_point(aes(x = trialCount, y = neutral, color = "Neutral"), size = 1.6) +
  labs(title = "Average Plot", x = "Trial", y = "Accuracy (%)") +
  scale_color_manual(values = c(Threat = "red", Neutral = "blue"))


# Print the average plot
print(plot)




#ADD THE INDIVIDUAL TRAJECTORIES ON TOP OF IT
#plot for average across subjects
plot_avg <- plot
plot_avg

# Iterate through each subject's data frame and add semi-transparent thin lines to the plot_avg
for (subject in unique_subjects) {
  # Get data frame for the current subject
  subject_df <- avg_check_answer_acc_df_list[[subject]]
  
  # Check the maximum trial count for the current subject
  if (max(subject_df$trialCount) != 4 && subject != "a3uv55hc87do9c") {
    # Add semi-transparent lines for the current subject to the plot_avg
    plot_avg <- plot_avg +
      geom_line(data = subject_df, aes(x = trialCount, y = threat), color = "red", alpha = 0.3) +
      geom_line(data = subject_df, aes(x = trialCount, y = neutral), color = "blue", alpha = 0.3)
  }
}

# Display the plot_avg
plot_avg
```
This plot shows the learning trajectory for the drag and drop task, with indiivdual learning trajectories plotted thinner and semi-transparent, and the average learning trajectory across participants with a thicker, more opaque line. We can see across trials, performance generally improves until they reach 100% and have met the conditions to learn it well enough to exit this task.
We can see, overall, that the individual learning trajectories differ for learning teh threat images versus the neutral images in some cases...(put this graph first)...is this learning of the threat images versus the neutral images in the structure significantly different?








